Use and acquisition of causal relations for decision making under uncertainty using imperfect information games

### 2018-08-16 Propuesta/Formato/Proposal_format.tex
Cambiando el Objetivo General

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
%\usepackage[spanish, mexico]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{listings}
\usepackage{breakcites}
\usepackage{dsfont}
\usepackage{hyperref}
\usepackage{amssymb,amsthm,amsmath,latexsym}
\usepackage[margin=1.5cm]{geometry}
\usepackage{natbib}
\usepackage{enumitem}
%\bibliographystyle{stylename}
%\usepackage{fancyhdr}
%\pagestyle{fancy}
\theoremstyle{plain}
\newtheorem{teo}{Theorem}
\newtheorem{prop}[teo]{Proposition}
\newtheorem{defi}[teo]{Definition}
\newtheorem{obs}[teo]{Observation}
\newtheorem{lem}[teo]{Lemma}
\newtheorem{cor}[teo]{Corolary}
\usepackage[pdftex]{color,graphicx}
\usepackage{tikz}
\usetikzlibrary{trees}
\usetikzlibrary{calc}
%\newcommand{\sgn}{\mathop{\mathrm{sgn}}}
\title{Use and acquisition of causal relations for decision making under uncertainty using imperfect information games}
\author{Mauricio Gonzalez Soto}
\begin{document}
%\nocite{*}
\maketitle
\tableofcontents
\newpage
\begin{abstract}
We consider decision problems under uncertainty where the options available to a decision maker and the resulting outcome are related through a causal mechanism which is unknown to the decision maker, although he is aware of the causal nature of his environment. We study how a decision maker can learn about this causal mechanism through sequential decision making as well as using current causal knowledge inside each round in order to make better choices had he not considered causal knowledge. We propose a decision making procedure in which an agent holds \textit{beliefs} about her environment which are used to make a choice and then are updated using the observed outcome. As proof of concept, we present an implementation of this causal decision making model and apply it to a simple problem. We show that the model achieves a performance similar to the classic Q-learning while it also acquires a causal model of the environment. 
\end{abstract}
\section{Introduction}
\indent A fundamental part of intelligent reasoning is being able to make decisions under uncertain conditions (\cite{danks2014unifying}, \cite{lake2017building}, \cite{pearlwhy}). Uncertain conditions mean that given a set of available choices, a decision maker can not predict the effect of the his choices. Because of this, the decision maker must take into consideration the stochastic relation between actions and consequences. From the von Neumann-Morgenstern decision making theory we know that when a rational\footnote{To be explained in full detail later.} decision maker knows this stochastic relation, then he must\textit{If rationality is assumed} choose the action that maximizes the \textit{expected utility} of a \textit{utility function} whose existence is guaranteed (\cite{von1944theory}). On the other hand, when a rational decision maker does not know the probabilities of the ocurrence of certain outcomes, or consequences, given his actions, then he must encode his personal, subjective, quantifications of any uncertainties in a probability distribution $p$ and choose the action that maximizes expected utility with respect to this probability (\cite{savage1954the}, \cite{bernardo2000bayesian}, \cite{gilboa2009decision}). If the current \textit{knowledge} of a decision maker is not enough to make good choices, then the decision maker can \textit{learn} from the environment by interacting with it in order to update his quantifications of uncertainty (\cite{bernardo2000bayesian}, \cite{peterson2017introduction}).

@@

Once the main problem has been stated, we proceed in Section \ref{Related_Work} to show previous attempts over this and similar problems. 
\newpage
\section{Main Concepts}{\label{Main_Concepts}}
	\subsection{Attempts to define Causality}
	Causality has been a difficult concept to define and several attempts have been made. In fact, in mainstream statistics the term \textit{cause} have been nearly banned as documented by \cite{pearl2018why}.

@@

@@

%\subsubsection{Repeated Games}
%\subsubsection{Learning in Games}

@@

	\subsection{Research Question}
	How a rational decision maker who faces an uncertain environment which is governed by a causal mechanism can learn and make use of this causal structure in order to make good choices? How can a causal structure help a decision maker in order to guide his learning process?
	\subsection{Hypothesis}
	Let $\mathcal{G}$ a causal graphical model and let $(\mathcal{A},\mathcal{E},\mathcal{C})$ a decision problem whose actions $a_i = \{ c_j | E_j : j \in J \}$  are causally related to consequences $c \in \mathcal{C}$ through the uncertain events $E \in \mathcal{E}$ which correspond to variables in $\mathcal{G}$. Then, if a decision maker doesn't know the probabilities of the uncertain events in $E$, by repeatedly making decisions he can learn a causal model of the environment and use it to find the optimal action (in the sense of expected utility theory) in less, or equal, rounds than if he doesn't consider causal information.
	\subsection{Objectives}
		\subsubsection{General Objectives}
			The proposed research has as a general objective to find how a rational autonomous agent who faces an uncertain environment can discover and use causal information in order to make good choices that maximize the expected utility for the decision maker.
		\subsubsection{Specific Objectives}
		\begin{enumerate}
		\item In order to achieve the general objective, we need to separate it into smaller problems which are required to be solved first. In first place, it is required to find a general way of defining a game that captures the interaction between a decision maker and a causal-governed environment.

@@

\newpage
\section{Related Work}
Reinforcement Learning (RL) has been the standard setting for decision-making and learning by interaction. In this setting it is assumed that a Markov Decision Process (MDP) is able to capture the effects of the agent's actions in the environment. An MDP is composed by a set of states, a transition function and a reward function, where an agent's action moves the state of the environment according to the transition function and obtaining a reward in such process.

@@

An attempt to formalize Decision Theory in the presence of Causal Information was attempted by Joyce, who concluded that a decision maker must choose whatever action is more likely to (causally) produce desired outcomes (\cite{joyce1999foundations}, \cite{peterson2017introduction}). His formulation falls short since he does not consider any kind of formal causal model beyond what is commonly understood by causality, although he captured the intuition that causal relations may be used to control the environment and to predict what is caused by the actions of a decision maker.

We are considering decision problems where an agent must choose some available action and then receive a reward from it. After a certain number of learning rounds, the agent is expected to output a good action. Problems of this nature are called \textit{bandit} problems (\cite{sutton1998reinforcement}). It has been shown that the probability of the action selected in the $n$-th round not being optimal has an upper bound (\cite{audibert2010best}) if the optimality criteria is choosen to be the \textit{minimal regret} which is basically the difference of the theoretical mean reward of the optimal action and the chosen action. On the other hand, if the largest mean reward is desired with a fixed confidence of $\delta$ then an algorithm for finding the optimal action exist in such a way that the number of rounds to find it is within a constant factor of a lower bound (\cite{jamieson2014lil}).  If one does not consider a fixed confidence but instead a fixed number of learning rounds (known as fixed budget), then we face a \textit{fixed budget} problem where a lower bound for the probability of finding the optimal arm is given by \cite{carpentier2016tight}.

@@

@@

The chosen actions will be compared to classic on-line decision making 
\subsubsection{Internal Validation: Reproducibility}
For the results obtained by following the methodology described in previous sections be reproducible, the causal model used to simulate an environment must be fully specified by describing the probabilistic parameters that control it. The initial distributions given to the decision maker to encode his beliefs must be shown as well with the updating criteria used when information from the environment becomes available. 
\subsubsection{External Validation: Different problems}
For the proposed method to be tested in different decision problems, it is required that the correspondent causal model satisfies all of the conditions previously described, and any derived algorithm will be designed in such a way that the characteristics of the causal model are an external input. In this way, if an external user is able to give a causal model, the method is expected to work independent of the particularities of the causal model which is being tested.
\subsubsection{Concurrent Validation}
Concurrent validation will be tested by comparing the performance obtained by the proposed method against the theoretical optima.
\subsection{Working plan}
Concrete steps towards solving the problem:
\begin{itemize}
\item Literature review, understanding the problem, considering several models and possible solutions.
\item Formalize the model.
\item Studying implications of the assumption of rationality in decisiom making under uncertainty in causal environments.
\item Propose a representation of beliefs that allow causal structure to be considered.
\item Updating criteria for beliefs.
\item Discovery of causal structure

\end{itemize}
\subsubsection{Publications plan}
\begin{itemize}
\item \textbf{Year 1:} Gonzalez-Soto, M., Sucar, L.E., Escalante, H.J., \textbf{Playing against Nature: causal discovery for decision making under uncertainty}. Accepted for a poster presentation at the CausalML 2018 workshop at ICML / IJCAI / AAMAS 2018. July 15 2018, Stockholm, Sweden. This can be confirmed at \url{https://sites.google.com/site/faim18wscausalml/program-schedule}. The paper can be found at \url{https://arxiv.org/abs/1807.01268}.
\item \textbf{Year 2:} Conference Paper
		\begin{itemize}
			\item Aim: Develop a Bayesian Non-parametric prior and updating procedure for beliefs about causal graphs in order to extend previous paper.
		\end{itemize}
\item \textbf{Year 3:} Journal Paper
		\begin{itemize}
			\item Aim: Theoretical paper of results for on-line causal learning.
		\end{itemize}
\end{itemize}

@@

\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[scale=0.5]{/Users/MauricioGS1/INAOE/Segundo_Semestre/Seminario/Semana12/codigo/causal_graph.png}}
\caption{Causal graphical model for the test scenario: the target variable \textit{Lives} is causally influenced by the disease the patient has, the treatment assigned and the survival to the secondary effects of treatment.}
\label{causal_model}
\end{center}
\vskip -0.2in
\end{figure}

@@

\begin{center}
\begin{minipage}{0.48\linewidth}
\includegraphics[width=\linewidth]{/Users/MauricioGS1/INAOE/Segundo_Semestre/CausalML_Workshop/figures/20_rounds_format.png}
\captionof{figure}{Average reward in 20 rounds}
\end{minipage}%
\hfill
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{/Users/MauricioGS1/INAOE/Segundo_Semestre/CausalML_Workshop/figures/50_rounds_format.png}
\captionof{figure}{Average reward in 50 rounds}
\end{minipage}
\end{center}
\begin{center}
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{/Users/MauricioGS1/INAOE/Segundo_Semestre/CausalML_Workshop/figures/100_rounds_format.png}
\captionof{figure}{Average reward in 100 rounds}
\end{minipage}
\hfill
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{/Users/MauricioGS1/INAOE/Segundo_Semestre/CausalML_Workshop/figures/200_rounds_format.png}
\captionof{figure}{Average reward in 200 rounds}
\end{minipage}
\end{center}

@@

%In Figure \ref{20_rounds} we observe the average rewards for each agent in 20 rounds of decision making. Here we notice that Q-learning outperforms our algorithm, which has a similar performance as the random choosin procedure until round 11.
%
%\begin{figure}[ht]
%\vskip 0.2in
%\begin{center}
%\centerline{\includegraphics[scale=0.5]{/Users/MauricioGS1/INAOE/Segundo_Semestre/CausalML_Workshop/figures/20_rounds_format.png}}
%\caption{Average reward obtained in each round for each agent}
%\label{20_rounds}
%\end{center}
%\vskip -0.2in
%\end{figure}
%
%In Figure \ref{50_rounds} we observe the average rewards for each agent in 50 rounds of decision making. Our algorithm follow closely the Q-learning agent and outperform the random agent.
%
%\begin{figure}[ht]
%\vskip 0.2in
%\begin{center}
%\centerline{\includegraphics[scale=0.5]{/Users/MauricioGS1/INAOE/Segundo_Semestre/CausalML_Workshop/figures/50_rounds_format.png}}
%\caption{Average reward obtained in each round for each agent}
%\label{50_rounds}
%\end{center}
%\vskip -0.2in
%\end{figure}
%
%In Figure \ref{100_rounds} we observe the average reward obtained by the three agents in 100 rounds, where our algorithm slightly outperforms Q-Learning.
%
%\begin{figure}[ht]
%\vskip 0.2in
%\begin{center}
%\centerline{\includegraphics[scale=0.5]{/Users/MauricioGS1/INAOE/Segundo_Semestre/CausalML_Workshop/figures/100_rounds_format.png}}
%\caption{Average reward obtained in each round for each agent}
%\label{100_rounds}
%\end{center}
%\vskip -0.2in
%\end{figure}
%
%In Figure \ref{200_rounds} we observe the average reward obtained by the three agents in 200 rounds. The average reward obtained is very similar for Q-learning and our algorithm.
%
%\begin{figure}[ht]
%\vskip 0.2in
%\begin{center}
%\centerline{\includegraphics[scale=0.5]{/Users/MauricioGS1/INAOE/Segundo_Semestre/CausalML_Workshop/figures/200_rounds_format.png}}
%\caption{Average reward obtained in each round for each agent}
%\label{200_rounds}
%\end{center}
%\vskip -0.2in
%\end{figure}

We see that our method obtains a very similar reward as the classic Q-learning algorithm for a larger number of rounds, where the random agent is outperformed, but our model offers something extra because it learns a causal model of the environment.

\newpage
\bibliographystyle{apalike}
\bibliography{/Users/MauricioGS1/INAOE/Propuesta/Bibliografia.bib}
\end{document}

>>>>

\documentclass[english,letterpaper,12pt,final]{article}
\usepackage{graphicx}
\usepackage{etex}

\sloppy
%\special{papersize=8.5in,11in}% This command prevents the use of other paper size in the dvi2ps conversion
%------Document properties------------
\usepackage{setspace}
\usepackage{pgfgantt}
\usepackage{enumitem}
%------math packages-------------------
\usepackage{amsthm}
\usepackage{tkz-berge} % Drawing graphs
%------algorithms packages-------------------
%\usepackage[ruled,vlined]{basic/algorithm2e}
\usepackage[noline,linesnumbered,noend]{algorithm2e}
%\linesnumbered
%------bibliography packages-----------
\usepackage{natbib}

\usepackage[utf8]{inputenc}

\usepackage[font=small,labelfont=bf]{caption}
\usepackage{listings}
\usepackage{breakcites}
\usepackage{dsfont}
\usepackage{hyperref}
\usepackage{amssymb,amsthm,amsmath,latexsym}

\usepackage{natbib}

\newcommand{\indep}{\rotatebox[origin=c]{90}{$\models$}}
\newcommand{\leci}{<\!\!\!\!\!\!\!\bigcirc}
%\newcommand{\lessint}{$\bigcirc$}
%------corporative identity of INAOE---
\usepackage{eso-pic}
\usepackage{pstricks}
\usepackage{INAOEMacros}

\usepackage{dsfont}
\usepackage{lineno,hyperref}

\usepackage{amssymb}
\usepackage{pifont}
\usepackage{url}
\usepackage{array}
%\usepackage{subfigure}
\usepackage{lscape}
\usepackage{amsfonts}
\usepackage{amsmath}

\usepackage[normalem]{ulem}
\usepackage{color}
\usepackage{multirow}
%\usepackage{mathtools}

%\usepackage[dvipdfmx]{graphicx} 
%\usepackage{bmpsize}

\usepackage{caption}
\usepackage{subcaption}
%------floating -----------------------
\usepackage{float}
\floatstyle{plain}
\newfloat{codigo}{thp}{lop}[section]
\floatname{codigo}{Algorithm}
\usepackage{booktabs}
%
%usepackage{lscape}
%\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{tablefootnote}
%------figure packages--------------
%\usepackage{subfigure}

%------page layout---------------------
\oddsidemargin 0.36cm
\evensidemargin 0.36cm
\marginparwidth 0.0cm
\textwidth 16.80cm

\topmargin -1.5cm
\headheight 1.0cm
\headsep 1.0cm
\footskip 1.0cm
\textheight 22.34cm

%\theoremstyle{plain}
%\newtheorem{teo}{Theorem}
%\newtheorem{prop}[teo]{Proposition}
%\newtheorem{defi}[teo]{Definition}
%\newtheorem{obs}[teo]{Observation}
%\newtheorem{lem}[teo]{Lemma}
%\newtheorem{cor}[teo]{Corolary}

%\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{56}}%
\theoremstyle{definition}
\newtheorem{rmk}{Definition}[section]
\newtheorem{teo}{Theorem}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{cor}{Corollary}[section]
\newtheorem{problem}{Problem}
\newtheorem{defi}{Definition}[section]
\newtheorem{pf}{Proof}
\newtheorem{pot}{Proof of Theorem \ref{thm2}}

%----------myDeclarations------------
\DeclareMathOperator*{\argmin}{argmin}
\definecolor{blue1}{rgb}{0.58,0.70,0.84}
\definecolor{blue2}{rgb}{0.93,0.95,1.0}
\usepackage{xcolor,colortbl}
\usepackage{titlesec}
\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

%-----end of preamble------------------
\pagenumbering{roman}
\begin{document}

% Title page
\input{gfrontpage}
%\doublespacing
\singlespacing
\tableofcontents
\newpage
\begin{abstract}
We consider decision problems under uncertainty where the options available to a decision maker and the resulting outcome are related through a causal mechanism which is unknown to the decision maker, although he is aware of the causal nature of his environment. We study how a decision maker can learn about this causal mechanism through sequential decision making as well as using current causal knowledge inside each round in order to make better choices had he not considered causal knowledge. We propose a decision making procedure in which an agent holds \textit{beliefs} about her environment which are used to make a choice and then are updated using the observed outcome. As proof of concept, we present an implementation of this causal decision making model and apply it to a simple problem. We show that the model achieves a performance similar to the classic Q-learning while it also acquires a causal model of the environment. 
\end{abstract}
\section{Introduction}
\indent A fundamental part of intelligent reasoning is being able to make decisions under uncertain conditions (\cite{danks2014unifying}, \cite{lake2017building}, \cite{pearlwhy}). Uncertain conditions mean that given a set of available choices, a decision maker can not predict the effect of the his choices. Because of this, the decision maker must take into consideration the stochastic relation between actions and consequences. From the von Neumann-Morgenstern decision making theory we know that when a rational\footnote{To be explained in full detail later.} decision maker knows this stochastic relation, then he must\textit{If rationality is assumed} choose the action that maximizes the \textit{expected utility} of a \textit{utility function} whose existence is guaranteed (\cite{von1944theory}). On the other hand, when a rational decision maker does not know the probabilities of the ocurrence of certain outcomes, or consequences, given his actions, then he must encode his personal, subjective, quantifications of any uncertainties in a probability distribution $p$ and choose the action that maximizes expected utility with respect to this probability (\cite{savage1954the}, \cite{bernardo2000bayesian}, \cite{gilboa2009decision}). If the current \textit{knowledge} of a decision maker is not enough to make good choices, then the decision maker can \textit{learn} from the environment by interacting with it in order to update his quantifications of uncertainty (\cite{bernardo2000bayesian}, \cite{peterson2017introduction}).

@@

Once the main problem has been stated, we proceed in Section \ref{Related_Work} to show previous attempts over this and similar problems.

\newpage
\section{Main Concepts}{\label{Main_Concepts}}
	\subsection{Attempts to define Causality}
	Causality has been a difficult concept to define and several attempts have been made. In fact, in mainstream statistics the term \textit{cause} have been nearly banned as documented by \cite{pearl2018why}.

@@

\subsubsection{Use of Causal Graphical Models over other causal models}
We choose to use specifically a Causal Graphical model because of the mathematical machinery that exists around them and because Graphs are a model of Cognitive Processes, such as causal reasoning (\cite{glymour2003learning}, \cite{danks2014unifying}). In this way, if an agent \textit{knows} that a certain environment is governed by causal relations, then a causal graphical model can be used to model the causal reasoning of the agent.

@@

@@

	\subsection{Research Question}
	How a rational decision maker who faces an uncertain environment which is governed by a causal mechanism can learn and make use of this causal structure in order to make good choices? How can a causal structure help a decision maker in order to guide his learning process? What does the rationality assumption implies about how to choose when considering causal information? How to trade off exploration and exploitation when trying to learn about the causal structure of an environment while also trying to make good choices?
	\subsection{Hypothesis}
	Let $\mathcal{G}$ a causal graphical model and let $(\mathcal{A},\mathcal{E},\mathcal{C})$ a decision problem whose actions $a_i = \{ c_j | E_j : j \in J \}$  are causally related to consequences $c \in \mathcal{C}$ through the uncertain events $E \in \mathcal{E}$ which correspond to variables in $\mathcal{G}$. Then, if a decision maker doesn't know the probabilities of the uncertain events in $E$, by repeatedly making decisions he can learn a causal model of the environment and use it to find the optimal action (in the sense of expected utility theory) in less, or equal, rounds than if he doesn't consider causal information.
	\subsection{Objectives}
		\subsubsection{General Objectives}
			The proposed research has as a general objective to understand what are the implications of causality for rational decision maker who faces an uncertain environment and how causal relations can be discovered and used in order to make good choices that maximize the expected utility for the decision maker.
		\subsubsection{Specific Objectives}
		\begin{enumerate}
		\item In order to achieve the general objective, we need to separate it into smaller problems which are required to be solved first. In first place, it is required to find a general way of defining a game that captures the interaction between a decision maker and a causal-governed environment.

@@

Reinforcement Learning (RL) has been the standard setting for decision-making and learning by interaction. In this setting it is assumed that a Markov Decision Process (MDP) is able to capture the effects of the agent's actions in the environment. An MDP is composed by a set of states, a transition function and a reward function, where an agent's action moves the state of the environment according to the transition function and obtaining a reward in such process.

@@

An attempt to formalize Decision Theory in the presence of Causal Information was attempted by Joyce, who stated that a decision maker must choose whatever action is more likely to (causally) produce desired outcomes (\cite{joyce1999foundations}, \cite{peterson2017introduction}). His formulation falls short since he does not consider any kind of formal causal model beyond what is commonly understood by causality, although he captured the intuition that causal relations may be used to control the environment and to predict what is caused by the actions of a decision maker. In his formulation of a Causal Decision Problem, he uses the \textit{probability of causing certain effect with an action}, which we refine here with the machinery of Pearl's Do-Calculus and Spirtes' definition of Causality.

In the class of decision problems considered for this proposal it is assumed that the a rational agent must choose some available action and then receive a reward from it. In the case where the agent does not has enough information available, we consider a certain number of learning rounds and expect the agent to output a good action. Problems of this nature have been modelled as \textit{bandit} problems (\cite{sutton1998reinforcement}). A bandit is an analogy of a \textit{slot machine} as the ones found in Las Vegas, where a lever is pulled an some monetary reward (probably cero) is observed. A bandit problem consists by a set of available actions (the arms of the slot machine) and a reward function. It has been shown that the probability of the action selected in the $n$-th round not being optimal has an upper bound (\cite{audibert2010best}) if the optimality criteria is choosen to be the \textit{minimal regret} which is basically the difference of the theoretical mean reward of the optimal action and the chosen action. On the other hand, if the largest mean reward is desired with a fixed confidence of $\delta$ then an algorithm for finding the optimal action exist in such a way that the number of rounds to find it is within a constant factor of a lower bound (\cite{jamieson2014lil}).  If one does not consider a fixed confidence but instead a fixed number of learning rounds (known as fixed budget), then we face a \textit{fixed budget} problem where a lower bound for the probability of finding the optimal arm is given by \cite{carpentier2016tight}.

@@

\subsection{Balancing exploitationd and exploration}
When the model is to be discovered, such as in the general case mentioned before, an agent must choose also between keep making an intervention in a variable that is known to cause a desired output or to explore for new variables that could bring even better rewards, but at the cost of not having best performance while looking out for them; this is known as the exploration vs exploitation dilemma (\cite{sutton1998reinforcement}). This question is to be attacked using the concept of \textit{mixed strategy} in a game. A mixed strategy is a probability distribution over available actions for an agent, so similarly to the $\varepsilon$-greedy methods in Reinforcement Learning we allow for some actions to be randomly choosen in order to explore further possibilities.

@@

The chosen actions will be compared to classic on-line decision making 
\subsubsection{Internal Validation: Reproducibility}
For the results obtained by following the methodology described in previous sections be reproducible, the causal model used to simulate an environment must be fully specified by describing the probabilistic parameters that control it. The initial distributions given to the decision maker to encode his beliefs must be shown as well with the updating criteria used when information from the environment becomes available. 
\subsubsection{External Validation: Different problems}
For the proposed method to be tested in different decision problems, it is required that the correspondent causal model satisfies all of the conditions previously described, and any derived algorithm will be designed in such a way that the characteristics of the causal model are an external input. In this way, if an external user is able to give a causal model, the method is expected to work independent of the particularities of the causal model which is being tested.
\subsubsection{Concurrent Validation}
Concurrent validation will be tested by comparing the performance obtained by the proposed method against the theoretical optima.
\subsection{Working plan}
Concrete steps towards solving the problem:
\begin{itemize}
\item Literature review, understanding the problem, considering several models and possible solutions.
\item Formalization of a Causal Decision Problem when causal relations are encoded into a Causal Graphical Model.
\item Studying implications of the rationality assumption for decisiom making under uncertainty in causal environments.
\item Propose a representation of beliefs that allow causal structure to be considered. Three subcases considered
\item Updating criteria for beliefs.
\item Discovery of causal structure.
\item Considering interventions in more than one variable.

\end{itemize}
\subsubsection{Publications plan}
\begin{itemize}
\item \textbf{Year 1:} Gonzalez-Soto, M., Sucar, L.E., Escalante, H.J., \textbf{Playing against Nature: causal discovery for decision making under uncertainty}. Accepted for a poster presentation at the CausalML 2018 workshop at ICML / IJCAI / AAMAS 2018. July 15 2018, Stockholm, Sweden. This can be confirmed at \url{https://sites.google.com/site/faim18wscausalml/program-schedule}. The paper can be found at \url{https://arxiv.org/abs/1807.01268}.
\item \textbf{Year 2:} Conference Paper
		\begin{itemize}
			\item When a causal model is unknown, how to encode uncertainties about causal structure in a probabilistic distribution? Bayesian Nonparametric prior that explicitly represents causal structure.
		\end{itemize}
\item \textbf{Year 2:} Conference Paper
	\begin{itemize}
		\item Using game-theoretical aspects for balancing exporation and exploitation for causal discovery. 
	\end{itemize}
\item \textbf{Year 3:} Journal Paper
		\begin{itemize}
			\item Aim: Theoretical paper of results for on-line causal learning.
		\end{itemize}
\end{itemize}

@@

\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=0.7\textwidth]{/Users/MauricioGS1/INAOE/Propuesta/Formato/figures/causal_graph.eps}}
\caption{Causal graphical model for the test scenario: the target variable \textit{Lives} is causally influenced by the disease the patient has, the treatment assigned and the survival to the secondary effects of treatment.}
\label{causal_model}
\end{center}
\vskip -0.2in
\end{figure}

@@

\begin{center}
\begin{minipage}{0.48\linewidth}
\includegraphics[width=\linewidth]{/Users/MauricioGS1/INAOE/Propuesta/Formato/figures/20_rounds_format.eps}
\captionof{figure}{Average reward in 20 rounds}
\end{minipage}%
\hfill
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{/Users/MauricioGS1/INAOE/Propuesta/Formato/figures/50_rounds_format.eps}
\captionof{figure}{Average reward in 50 rounds}
\end{minipage}
\end{center}
\begin{center}
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{/Users/MauricioGS1/INAOE/Propuesta/Formato/figures/100_rounds_format.eps}
\captionof{figure}{Average reward in 100 rounds}
\end{minipage}
\hfill
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{/Users/MauricioGS1/INAOE/Propuesta/Formato/figures/200_rounds_format.eps}
\captionof{figure}{Average reward in 200 rounds}
\end{minipage}
\end{center}

@@

%------------- References --------------------
\singlespacing
%doi=false,isbn=false,url=false
\bibliographystyle{apalike}
\bibliography{/Users/MauricioGS1/INAOE/Propuesta/Bibliografia.bib}

%------------- References --------------------

\end{document}
